Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
hello world in progress

Let us illustrate the use of Infergo on a basic example serving
as a probabilistic programming equivalent of the "Hello, World!"
program --- inferring parameters of a unidimensional Normal
distribution. In this example, the model holds the set of
samples from which the distribution parameters are to be
inferred:
\begin{lstlisting}
type Model struct {
    Data []float64
}
\end{lstlisting}

// x[0] is the mean,
// x[1] is the log stddev of the distribution
func (m *Model) Observe(x []float64) float64 {
    // Our prior is a unit normal ...
    ll := Normal.Logps(0, 1, x...)
    // ... but the posterior is based 
	// on data observations.
	ll += Normal.Logps(x[0], math.Exp(x[1]),
	                   m.Data...)
    return ll
}
\end{lstlisting}

@@

\section*{Acknowledgements}

% The author owes a debt of gratitude to Frank Wood who introduced
% the author to probabilistic programming and inspired to
% pursue probabilistic programming paradigms and applications. The
% author also would like to thank Jan-Willem van de Meent, with
% whom the author had fruitful discussions of motives, ideas, and
% implementation choices behind Infergo, and whose thoughts and
% recommendations significantly influenced Infergo design.
% Finally, the author thanks PUB+, the company the author works
% for, for supporting development of Infergo and letting the
% author experiment with applying probabilistic programming to
% critical decision-making in production environment.

>>>>

Let us illustrate the use of Infergo on a basic example serving
as a probabilistic programming equivalent of the "Hello, World!"
program --- inferring parameters of a unidimensional Normal
distribution. In this example, the model object holds the set of
observations from which the distribution parameters are to be
inferred:
\begin{lstlisting}
type Model struct {
    Data []float64
}
\end{lstlisting}

The \lstinline{Observe} method computes the log-likelihood of
the distribution parameters. The Normal distribution has two
parameters: mean $\mu$ and standard deviation
$\sigma$. To ease the inference, positive $\sigma$ is transformed to
unrestricted $\log \sigma$, and the parameter vector is $[\mu,
\log \sigma]$. \lstinline{Observe} first imposes a prior on the
parameters, and then conditions the posterior distribution on
the observations:

\begin{lstlisting}
// x[0] is the mean,
// x[1] is the log stddev of the distribution
func (m *Model) Observe(x []float64) float64 {
    // Our prior is a unit normal ...
    ll := Normal.Logps(0, 1, x...)
    // ... but the posterior is based 
	// on data observations.
	ll += Normal.Logps(x[0], math.Exp(x[1]),
	                   m.Data...)
    return ll
}
\end{lstlisting}

@@
